\documentclass{article}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{geometry}
\geometry{margin=1in}
\begin{document}

\section{Comparison of Auction Algorithms}

\subsection{Nima-McAfee Auction}
\begin{algorithm}[htbp]
\DontPrintSemicolon
Sort sellers ascending: $v^S_{1}<v^S_{2}<\dots<v^S_{n}$

\Sort buyers descending: $v^B_{1}>v^B_{2}>\dots>v^B_{m}$

Find largest $L$ and $K$ satisfying:
$v^B_{L}\ge v^S_{L}$, and $\sum_{i=1}^{L} q_{B_i}\le \sum_{i=1}^{K} q_{S_i}$

\BlankLine
$\gamma \leftarrow \frac{1}{2}(v^S_{L+1}+v^B_{K+1})$

\uIf{$\gamma \in [v^S_{L}, v^B_{K}]$}{
    $\Theta_{\text{Pr}}\leftarrow\min(\sum_{i=1}^{L} q_{B_i}, \sum_{i=1}^{K} q_{S_i})$

    Set uniform trade price: $p = \gamma$
}
\Else{
$\Theta_{Pr}\leftarrow\min(\sum_{i=1}^{L-1} q_{B_i}, \sum_{i=1}^{K-1} q_{S_i})$

Set buyer price: $p_B = v^B_L$, and seller price: $p = v^S_{L}$
}
\caption{Nima-McAfee Auction}
\label{alg:nima_mcafee}
\end{algorithm}


\subsection{SBBA Auction}
\begin{algorithm}[htbp]
\DontPrintSemicolon
Sort buyers descending: $b_1 \geq b_2 \geq \dots \geq b_n$

Sort sellers ascending: $s_1 \leq s_2 \leq \dots \leq s_n$

\BlankLine
Find largest $k$ s.t. $b_k \geq s_k$

\uIf{$s_{k+1}\leq b_k$}{
    Set price $p \leftarrow s_{k+1}$

    Trade all $k$ matched pairs at price $p$
}
\Else{
    Set price $p \leftarrow b_k$

    Randomly exclude one seller among cheapest $k$ sellers

    Trade remaining $k-1$ matched pairs at price $p$
}
\caption{SBBA Auction (Strongly Budget Balanced)}
\label{alg:sbba}
\end{algorithm}


\subsection{MUDA Auction}
\begin{algorithm}[htbp]
\DontPrintSemicolon
Randomly partition buyers into two groups: $B_1, B_2$

Randomly partition sellers into two groups: $S_1, S_2$

Compute prices:
$p_1 \leftarrow$ market-clearing price for $(B_1,S_1)$

$p_2 \leftarrow$ market-clearing price:
$(B_2, S_2)$

Cross-match at computed prices:
\begin{itemize}
\item Match buyers $B_1$ with sellers $S_2$ at price $p_2$
\item Match buyers $B_2$ with sellers $S_1$ at price $p_1$
\end{itemize}

\label{alg:muda}
\caption{MUDA Double Auction (Segal-Halevi et al. \cite{SegalHalevi2017MUDA})}
\end{algorithm}

\section{Comparative Market Design Analysis}

\begin{itemize}
    \item \textbf{Price Formation:}
    \begin{itemize}
        \item \textbf{Nima-McAfee:} Uses the midpoint between the marginal unsuccessful buyer and seller valuations; sometimes results in a surplus.
        \item \textbf{SBBA:} Uses a single uniform price, strongly budget balanced; may randomly exclude one seller.
        \item \textbf{MUDA:} Uses random market partitioning and computes two cross-market prices, ensuring truthful behavior.
    \end{itemize}

        \item \textbf{Budget Balance:}
        \begin{itemize}
        \item \textbf{Nima-McAfee:} Weakly budget-balanced; can leave surplus.
        \item \textbf{SBBA:} Strongly budget-balanced; no surplus left.
        \item \textbf{MUDA:} Budget-balanced in expectation due to random partitions.
    \end{itemize}

    \end{itemize}

    \textbf{Truthfulness:} All algorithms ensure truthfulness.

\end{document}